Solar jet observed at the limb in SDO/SST

### 2016-07-28 paper/ms_temp_paper.tex
figure managment

@@

axcb = fig.colorbar(line_segments)
axcb.set_label('Time')
ax10.set_title('Slit across')
ax10.set_xlabel('Distance across slit')
ax10.set_ylabel('Velocity {}'.format(dop_fin.unit))
plt.sci(line_segments)
plt.draw()
plt.show()

>>>>

dopp_grid = texfigure.MultiFigure(2, 2, reference="Dop_Exam")

@@

axcb = fig.colorbar(line_segments)
axcb.set_label('Time')
ax10.set_title('Slit across')
ax10.set_xlabel('Distance across slit')
ax10.set_ylabel('Velocity {}'.format(dop_fin.unit))
plt.sci(line_segments)

dop_gird.placement = 't'
dop_grid.caption = 'Captiony things'

plt.draw()
plt.show()
